%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\newcommand*{\myfont}{\fontfamily{cmr}\selectfont}

%\addtolength{\topmargin}{-.35in}
\addtolength{\textheight}{0.7in}

\definecolor{gray}{HTML}{4D4D4D}

\usepackage{ifthen}
\newboolean{long}
%\usepackage[dvipsnames]{xcolor}

\begin{document}


\header{philip}{ball}{} % Your name and current job title/field


%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
74 Kings Drive, Surbiton, Surrey, KT58NH
philipjball93@gmail.com
+44 (0)7818 447174
\section{Languages}
native English speaker,
spoken Mandarin (fluent),
basic French
\section{Programming}
Python, C/C++, MATLAB, R, VBA, \textcolor{gray}{\begin{myfont}\LaTeX\ \end{myfont}}
\section{Web}
Site: \href{https://fiorenza2.github.io}{fiorenza2.github.io}
GitHub: \href{https://github.com/fiorenza2}{fiorenza2}
LinkedIn: \href{https://uk.linkedin.com/in/philipjohnball}{philipjohnball}
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{2017 -- 2018}
{The University of Cambridge}
{MPhil {\normalfont in Machine Learning, Speech and Language Technologies }}
{Cambridge, UK}
{Achieved Grade: Distinction (78.09\%)
	\begin{itemize}
        \item Dissertation entitled "Fairness in Machine Learning with Causal Reasoning", supervised by Dr. Adrian Weller (Programme Director for AI at the Alan Turing Institute). Awarded distinction (77\%).
        \item Produced a novel sensitivity analysis approach for counterfactual fairness and developed variational/adversarial training methodologies to learn counterfactually fair representations. 
        \item Completed courses including: Bayesian Machine Learning, NLP, Deep Learning, Computer Vision, Reinforcement Learning, Speech, Machine Translation.
        \item Elected the Student Representative for the MPhil course
	\end{itemize}}

%------------------------------------------------

%------------------------------------------------

\entry
{2011 -- 2015}
{The University of Oxford}
{MEng {\normalfont in Engineering Science}}
{Oxford, UK}
{Achieved Grade: First-Class Honours
	\begin{itemize}
		\item Achieved the top mark in the year for my 3rd Year Computing Project entitled `Wireless Communication Channels: Characterisation using Orthogonal Functions'.
		\ifthenelse{\boolean{long}}{\item 4th Year project in entitled `Modelling High Density Wireless Networks in a Finite Domain’, developing
        novel techniques using stochastic geometry to improve IEEE 802.11 standard wireless performance in high-density
        scenarios.}
		\item President of the Engineering Society in my 4th Year, with over 500 paying members and a mailing list with a reach of over 1,000. Led a record breaking £20,000+ sponsorship drive.
	\end{itemize}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}


\begin{entrylist}

%------------------------------------------------

\entry
{October 2018 -- Present}
{Microsoft Research}
{AI Resident}
{Cambridge, UK}
{Achievements:
\begin{itemize}
    \item Designing and researching deep reinforcement agents to play first-person shooter video games at state of the art levels.
    \item Refactoring distributed computational source code to ensure compatability with existing platforms.
\end{itemize}
}

\entry
{September 2015 -- September 2017}
{Accenture}
{Data Science Consultant}
{London, UK and Hong Kong}
{Achievements:
\begin{itemize}
    \item Promoted to Consultant in 1.5 years (average is 2.5 years)
    \item Advising a major bank on the Agile roll-out of a cloud analytics platform, providing data
    science and modelling support. Working in Hong Kong, designing and running workshops,
    as well as creating NLP and computer vision based PoCs in Python.
    \item Lead predictive modeller for the Accenture 6 Nations phone app, working in R with Opta
    data. Correctly predicted the ultimate tournament winner and beat book maker odds
    (using CARET, random forests, automated workflows etc.).
    \item Lead Data Scientist for a supply chain optimisation project for a major European steel
    manufacturer, leveraging association rules mining (ARM) to uncover hidden patterns in
    the steel ordering process. Determined over €6.5m in savings, resulting in a successful
    multi-million € sales bid.
    \ifthenelse{\boolean{long}}{}{\item Lead Business Analyst for a risk assessment and process automation work-stream in a
    major bank. Designed the To-Be process and automation framework from the ground
    up in VBA, whilst engaging with senior stakeholders globally across all lines of business.
    Improved compliance and saved FTEs.}
    
\end{itemize}}

%------------------------------------------------




%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	Awards section
%----------------------------------------------------------------------------------------
\pagebreak
\section{Awards}

\begin{entrylist}
	
	%------------------------------------------------
    \entrysmall{2019}
    {Hack Cambridge Main Competition: 1st Prize}
    {Major League Hacking}
    {Winner of the main annual Cambridge hackathon (over 300 participants), developing an in-browser private deep learning app to aid physiotherapy rehabilitation in TensorFlow.js.}
	
    \entrysmall
    {2018}
    {£2,000 Competition Finalist}
    {Cambridge University Entrepreneurs}
    {One of 4 finalists in the annual CUE university-wide entrepreneurial competition, looking for
    funding to found a biotech/ML start-up to treat IBDs.}
    
	\entrysmall
	{2015}
	{College Prize}
	{University College, University of Oxford}
	{Awarded in recognition of achieving 1st class results in finals examinations overall.}
    	
	\entrysmall
	{2012 -- 2014}
	{Scholarship {\normalfont for Academic Achievement}}
	{University College, University of Oxford}
	{Awarded in recognition of achieving 1st class results in 1st, 2nd and 3rd year examinations.}

	
	%------------------------------------------------
	
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

Piano (Grade 8 ABRSM), bass guitar, reading, gym, badminton, squash, travel.


%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\iffalse

\section{publications}

\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

\printbibsection{book}{books} % Print all books from the bibliography

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
\end{refsection}

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
\end{refsection}

\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------
\fi
\end{document}